Effectiveness of community-based TURF-reserves in small-scale fisheries

### 2018-12-04 docs/paper/Villasenor-Derbez.Rmd
Fixed text

<!-- While many ecology studies incporporate BACI\citep{stewartoaten_1986}, few MPA studies do the same. Importance of evidence-based conservation mediterranean and as a movement \{guidetti_2002,ferraro_2006}. Whole paragraph here. -->

@@

Before discussing our data collection methods and describing our analyses, our case studies warrant some more background. TURF-reserves can be created as community-based marine reserves, voluntarily established and enforced by local communities. This bottom-up approach increases compliance and self-enforcement, and reserves can yield benefits similar to systematically-designed reserves \citep{gelcich_2015-Gw,beger_2004-Y8,smallhornwest_2018}. Community-based spatial closures occur in different contexts, like the *kapu* or *ra’ui* areas in the Pacific Islands \citep{bohnsack_2004,johannes_2002}. However, marine reserves are difficult to enforce if they are not legally recognized, and fishers rely on the exclusive access granted by the TURF.

>>>>

@@

Before discussing our data collection methods and describing our analyses, our case studies warrant some more background. TURF-reserves can be created as community-based marine reserves, voluntarily established and enforced by local communities. This bottom-up approach increases compliance and self-enforcement, and reserves can yield benefits similar to systematically-designed reserves \citep{gelcich_2015,beger_2004,smallhornwest_2018}. Community-based spatial closures occur in different contexts, like the *kapu* or *ra’ui* areas in the Pacific Islands \citep{bohnsack_2004,johannes_2002}. However, marine reserves are difficult to enforce if they are not legally recognized, and fishers rely on the exclusive access granted by the TURF.
